SAT Competition 2020\tnoteref{title}

### 2021-02-02 paper/main.tex
structure

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020 
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of the tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition web pages (\url{https://satcompetition.github.io/2020/}). 
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results together with  a survey on the
the solving strategies implemented distinctly in  top-ranking  solvers. 
Going considerably beyond the plain competition rankings, we provide more in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers,  (Section~\ref{sec:analysis}.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.
\todo{Need to decide on final structure regarding the results overview and analysis}

@@

\section{Code-Bases and Winning Strategies}
\label{sec:analysis}

In the following, we provide an overview of the participating teams and solvers, 
and summarize new strategies which are implemented in the award winning solvers of this competition.

We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
Our review of the winning strategies in this competition starts with sequential (including incremental) SAT solving in Section~\ref{sec:part:seq}, then we continue with parallel SAT solving in Section~\ref{sec:part:par} and conclude with solvers in the cloud track in Section~\ref{sec:part:cloud}.

@@

\section{Differentiated Analysis of Main Track Results}

>>>>

This article focuses on the 2020 instantiation of the SAT competitions. 
To this end, we provide
a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
participating solvers, benchmarks, and the empirical results from the competition.
In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020 
in addition to the already earlier established main, parallel, and incremental tracks; we
provide motivation and the new organizational details for both of the tracks.
In terms of solvers, we provide an overview of solving strategies and other details implemented in top-performing solvers
from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings.
 As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
an overview of the benchmarks contributed to the 2020 competition.
In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}. 
Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.

The rest of this article is organized as follows. 
We start by providing an overview on the competition, including details on and motivations for the several
competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
in evaluating the competing solvers, 
and the computing environments used for executing the competition
(Section~\ref{sec:overview}).
We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
process used for constructing the sets (Section~\ref{sec:instances}).
In Section~\ref{sec:results} we provide an overview of the competition results %together with a survey on the
followed by a survey on 
the solving strategies implemented distinctly in top-ranking solvers in Section~\ref{sec:winners}. 
Going considerably beyond the plain competition rankings, in Section~\ref{sec:analysis}, we provide more in-depth analysis of the competition 
data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
of individual solvers to the ``virtual best solver'' and 
portfolios constructed from the competing solvers.
The article is concluded with future prospects in Section~\ref{sec:conclusion}.

@@

\section{Winning Solvers}
\label{sec:winners}

In the following, we provide an overview of the participating teams and solvers, 
and summarize new strategies which are implemented in the award winning solvers of this competition. 
We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
Our review of the winning strategies in this competition starts with sequential solvers in the Main-, Planning-, and Incremental Library track in Section~\ref{sec:part:seq}, then we continue with winners of the Parallel track in Section~\ref{sec:part:par} and conclude with winning solvers in the Cloud track in Section~\ref{sec:part:cloud}.

@@

\section{Differentiated Analysis of Main Track Results}
\label{sec:analysis}
